Carbonate chemistry at Ny-Ålesund

### 2021-08-24 awipev-CO2.Rmd
refine pCO2

#################### Function RMSE for model 2 regression root mean square error
#test <- readr::read_csv(file="test_file")
lm2 <- function(data = NULL, x, y) {
  col_x <- eval(substitute(x), data)
  col_y <- eval(substitute(y), data)
  col_x <- x
  col_y <- y
fit <- lmodel2(col_y ~ col_x, nperm = 99)
  intercept_MA <- fit$regression.results[2,2]
  slope_MA <- fit$regression.results[2,3]
  intercept_OLS <- fit$regression.results[1,2]
  slope_OLS <- fit$regression.results[1,3]
  predicted <- intercept_OLS + col_x * slope_OLS
  error <- col_x - predicted
  my_list <- list(fit = print(fit), rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
}

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Calculated vs Contros pCO2"
fit <- lmodel2(data = d_all,   pco2_calc_fb ~ pco2_fb, nperm = 99)
print(fit)
p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
  geom_point()+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
  #                    "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
```

The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).

```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

>>>>

#################### Function RMSE for model 2 regression root mean square error
#test <- readr::read_csv(file="test_file")
lm2 <- function(data = NULL, x, y) {
  col_x <- eval(substitute(x), data)
  col_y <- eval(substitute(y), data)
  col_x <- x
  col_y <- y
fit <- lmodel2(col_y ~ col_x, nperm = 99)
  intercept_MA <- fit$regression.results[2,2]
  slope_MA <- fit$regression.results[2,3]
  intercept_OLS <- fit$regression.results[1,2]
  slope_OLS <- fit$regression.results[1,3]
  predicted <- intercept_OLS + col_x * slope_OLS
  error <- col_x - predicted
  my_list <- list(intercept_MA = intercept_MA, 
                  slope_MA = slope_MA,
                  intercept_OLS = intercept_MA, 
                  slope_OLS = slope_MA,
                  rmse = sqrt(mean(error^2, na.rm=TRUE)))
  return(my_list)
}

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
title <- "pCO2 normalized at in situ temperature"
fit <- lmodel2(data = d_all,   pco2_calc_fb_insi_temp ~ pco2_fb_insi_temp, nperm = 99)
print(fit)
p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
  geom_point()+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
  #                    "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1, xlim=c(200,420), ylim=c(200,420))+
  labs(title = "", x="Measured pCO2", y="Calculated pCO2") + theme_bw()  
print(p)
ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
```

The relationship between the measured (Contros) and calculated pCO2 (blue line) is relatively poor. It is far from the 1:1 relationship (black dashed line). The slope is `r signif(fit$regression.results[2,3], 3)`) and its 95% confidence interval does include 1; r2 is `r round(fit$rsquare, digits=2)`.

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2

```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
# print(p)
# 
```
